\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-02-22 latex/egpaper_for_review.tex
Small changes algorithm part

\section{Grand Unified Edge Contraction Algorithm}
\begin{itemize}
\item Define graph formalism
\item Rows in the table:
\begin{itemize}
\item Mutex Watershed (MWS), [proof of equivalence included in Appendix]
\item Greedy Additive Edge Contraction (GAEC), 
\item Greedy Fixation (GF), 
\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) and weighted average (WPGMA) linkage criteria
\item GALA (learned update rule)
\item Something depending on the node size...?
\end{itemize}
\end{itemize}

>>>>

\section{Grand Unified Whatever Clustering}
\begin{itemize}
\item Define graph formalism and clustering $\Pi$
\item \TODO{Description of the algorithm}
\item Linkage criteria and table:
\begin{itemize}
\item Mutex Watershed (MWS), [proof of equivalence included in Appendix]
\item Greedy Additive Edge Contraction (GAEC), 
\item Greedy Fixation (GF), 
\item Hierarchical Agglomerative Clustering with single, complete, average (UPGMA) and weighted average (WPGMA) linkage criteria
\item GALA (learned update rule)
\item Something depending on the node size...?
\end{itemize}
\item Pseudocode does not (exactly) include more general options: size of the nodes, features for CNN, histogram for median \TODO{But I think I should keep it simple}
\item Comment about must-not-link relations: they give high proprity to the most confident repulsive edges \item I don't think I need to mention the merge tree (although it could be easily deduced from the code, as a sequence of clustering)
\item Define multicut energy (or move to following section)
\end{itemize}
